---
title: "Model Checking 2"
output: html_notebook
---

II. Assumptions on Error Violated
Brown-Forsythe Test (3.6)


```{r}
install.packages("MASS")
install.packages("HH")
```

```{r}
library(MASS)
library(HH)
```

EXAMPLE 1: 6.10 - Grocery Retailer
```{r}
gr <- read_table2("/Volumes/5ive3rds/CSULB/Classes/510/Data/Data Sets KN/KutnerData/Chapter  6 Data Sets/CH06PR09.txt", col_names = FALSE)
names(gr)<-c("y","x1","x2","x3")
```

```{r}
fitg<-lm(y~x1+x2+x3,data=gr)
plot(fitg)
```

Let's first use the "eye test" to determine our split point based on residual plot.

Next, we need to group our data based on this

```{r}
yc<-4600

indc<-as.factor(c(fitg$fitted.values>yc)) #extremely critical that we define this indicator as a FACTOR, otherwise code won't run!

#indm<-as.factor(c(fitg$fitted.values>median(fitg$fitted.values)))

gra<-cbind(gr,indc,fitg$fitted.values)
gra[indc==T,]
```

Perform the test
```{r}
HH::hovBF(y~indc,data=gra)
```


Box-Cox Transformation

Let's use this for the Market data set
```{r}
market <- read_csv("/Volumes/5ive3rds/CSULB/Classes/510/Data/ASCII-comma/Chapter 07/market.txt")

fit1<-lm(Y1~X1+X2+X3+X4, data=market)
```



```{r}
MASS::boxcox(fit1)
```
There should be a visible maximum if the algorithm converges. to see it, we may need to adjust our viewing window of $\lambda$ values:
```{r}
boxcox(fit1,lambda = seq(-10, 2, 1/10))
```

```{r}
boxcox(fit1,lambda = seq(-15, 2, 1/10))
```

Now we can compare and contrast the fit summary  before and after the transformation:
```{r}
summary(lm(Y1~X1+X2+X3+X4, data=market))
```

```{r}
summary(lm(Y1^-4~X1+X2+X3+X4, data=market))
```

For the Grocery retailer data, even though the BF test indicated homoscedasticity, it will be instructive to see how the p-value of the test changes as a result:

```{r}
boxcox(fitg,lambda = seq(-2, 10, 1/10))
```
This indicates 4 is a convenient value for $\lambda$ 
```{r}
hovBF(y~indc,data=gra)
hovBF(y^4~indc,data=gra)
```

